---
title: "Visualize Data"
author: "Jasmine Lantaca"
format: gfm
---


```{r}
#| label: setup
#| include: false
library(tidyverse)
```



## Your Turn 0

Add a setup chunk that loads the tidyverse packages.


```{r}
#| label: loading mpg data
mpg
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
#| label: making graph
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
#| label: making a boxplot
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#| label: making histogram
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#| label: binwidth added
ggplot(data = mpg) +
  geom_histogram(aes(x = hwy), 
                 binwidth = 2)
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
#| label: adding more aesthetics
ggplot(data = mpg) +
  geom_point(aes(x = displ, 
                 y = hwy,
                 color = class)) +
  labs(x = "Engine Size Displacement",
       y = "Highway Mileage (mpg)",
       color = "Class of Vehicle",
       title = "The Bigger the engine, the less mileage we get on the highway") +
  theme_light()
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
#| label: facets
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
# Creates four column through cyl with one row through a dot

q + facet_grid(drv ~ .)
# Creates three rows through drv with one column through a dot

q + facet_grid(drv ~ cyl)
# Creates three rows using drv combined with four columns with cy1

q + facet_wrap(~ class)
# Makes a graph for each class
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}
#| label: bargraph
ggplot(mpg) + 
  geom_bar(aes(x = class,
               fill = class)) +
  guides(fill = "none") +
  labs(x = " Class of Vehicle",
       y = "Number of Vehicles in Sample") +
  theme_bw()
```

## Quiz

What will this code do?

```{r}
#| label: JPG of Graph
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(aes(color = class)) +
  geom_smooth(color = "#49b9de",
              se = FALSE,
              method = "lm") 
# It will create a graph that is a scatter plot with a line, basically adding two geometries. 

  #ggsave("example.jpg", width = 6,height = 4)
# Saving an image in the folder. Basically, creates a image, especially a jpg image, of the given graph.
```


***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```